Appendix: Trends in age-adjusted mortality rates for blacks and whites by cause and sex, 1969-2013, United States

### 2017-03-30 Manuscript/Appendix-agestd-mort-rates.Rmd
add hoverinfo comments

```{r print-em, fig.width = 9, fig.height = 9, echo = F}
ggplotly(Cardiovascular.Male.mort.plot[[1]]) %>% layout(xaxis = list(title = "Year (1969-2013)"), showlegend = F) 
ggplotly(Cardiovascular.Male.mort.plot[[2]]) %>% layout(xaxis = list(title = "Year (1969-2013)"))
```

>>>>

```{r print-em, fig.width = 9, fig.height = 9, echo = F}
ggplotly(Cardiovascular.Male.mort.plot[[1]]) %>% layout(xaxis = list(title = "Year (1969-2013)"), showlegend = F) 
ggplotly(Cardiovascular.Male.mort.plot[[2]]) %>% layout(xaxis = list(title = "Year (1969-2013)"))

#manipulating hover info:
#p <- ggplotly(Cardiovascular.Male.mort.plot[[2]]) %>% layout(xaxis = list(title = "Year (1969-2013)"))
#p$x$data[[1]]$hoverinfo = "none" #if want no hover info for a particular trace
#p$x$data[[1]]$text #otherwise, modified what is stored here to display how you want it to look. 
```
